Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-12 final/paper/paper.tex
Grammar check results

One more results that we found was, having the ability to perform the four operations: 
Layer, Concat, Facet and Repeat, it gave user a better understanding of these 
operations and how to properly use then. The validation steps, along with the 
error message that Pleiades provides helps user to understand what they are doing 
wrong, helping them in their education about visualization in general.

In terms of exploring data, the time take to compose different charts and see 
find useful results, went down by a lot because of the high-level of interactivity 
provided. Users don’t have to worry about updating JSON code for ever 
small change in their chart.

@@

The key result for Pleiades was how easy it became to compose graph. During our presentation, 
we asked a lot of our peers to try out the our application and compare their workflow to that 
when they used the Vega-Lite API along with a JSON spec. The results were as we expected: 
Pleiades gives a better understanding and ease at composing different charts and see what fits the best.
The key-idea behind why Pleiades makes composing charts easier and more intuitive is because the 
process is bottom-up, whereas Vega-lite is top-down. Also, the graphical user interface provided 
used with a smother way to compose charts, than to write nested JSON specs.

>>>>

The key result for Pleiades was how easy it became to compose graph. 
During our presentation, we asked a lot of our peers to try out our 
application and compare their workflow to that when they used the 
Vega-Lite API along with a JSON spec. The results were as we expected: Pleiades 
gives a better understanding and ease at composing different charts and see
what fits the best. The key-idea behind why Pleiades makes composing charts 
easier and more intuitive is because the process is bottom-up, 
whereas Vega-lite is top-down. Also, the graphical user interface 
provided used with a smother way to compose charts, than to write nested JSON specs.

One more results that we found was, having the ability to perform 
the four operations: Layer, Concat, Facet and Repeat, it gave the user
a better understanding of these operations and how to properly use then. 
he validation steps, along with the error message that Pleiades provides 
helps users to understand what they are doing wrong, helping them in their 
education about visualization in general.

In terms of exploring data, the time it takes to compose different 
charts and see find useful results, went down by a lot because of the 
high-level of interactivity provided. Users don’t have to worry about 
updating JSON code for every small change in their chart.

@@
